ResultsNPS

### 2019-10-14 R/nps_reports/results.Rmd
refactored the NPS r scripts into a single directory with simpler names.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source('functions/graphs_NPS.R')
source('functions/datasets_NPS.R')
quant_max <- 0.95
size <- params$size

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source('nps_reports/graphs_NPS.R')
source('nps_reports/datasets_NPS.R')
quant_max <- 0.95
size <- params$size
